Ergo emission properties are defined by the following parameters in a monetary section of the config:

\begin{itemize}
    \item{\em fixedRatePeriod } - number of blocks since the genesis block, the reward won't change.
    For mainnet it equals to 525600, that corresponds to 2 years of fixed rate (assuming 2 minutes block interval)
    \item{\em fixedRate } - number of coins issued every block during the $fixedRatePeriod$.
    For mainnet it will be set to 7500000000 (75 coins with 8 digits).
    \item{\em epochLength } - number of blocks between reward reduction.
    For mainnet it will be set to 64800 (3 month).
    \item{\em oneEpochReduction } - number of coins reward decrease every epochs.
    For mainnet it will be set to 300000000 (3 coins with 8 digits).
\end{itemize}

Thus for the first $fixedRatePeriod$ blocks block reward for miner will be fixed and equals to $fixedRate$ \ergo{} coins,
after $fixedRatePeriod$ block reward will be reduced for $oneEpochReduction$ coins every $epochLength$ blocks.

Instead of having implicit emission rules via a special type of transaction (e.g. coinbase transaction in Bitcoin),
Ergo coins emission is defined explicitly by \Sigma-state transactional language.
All \ergo{} coins will be created in the genesis state, in an output protected by the following script:

\begin{minted}{java}
    let epoch = 1 + ((HEIGHT - fixedRatePeriod) / epochLength)
    let out = OUTPUTS(0)
    let coinsToIssue = if(HEIGHT < fixedRatePeriod) fixedRate else fixedRate - (oneEpochReduction * epoch)
    let correctCoinsConsumed = coinsToIssue == (SELF.value - out.value)
    let sameScriptRule = SELF.propositionBytes == out.propositionBytes
    let heightIncreased = HEIGHT > SELF.R3[Long].value
    let heightCorrect = out.R3[Long].value == HEIGHT
    let lastCoins = SELF.value <= oneEpochReduction
    (correctCoinsConsumed && heightCorrect && heightIncreased && sameScriptRule)) || (heightIncreased && lastCoins)
\end{minted}

This protection script allows miner to take only a part of all coins, corresponding to current block reward.
Fist, this script calculates $coinsToIssue$ - number of coins, current miner takes to himself,
and checks, that the remaining  number of coins in the first output $out$ equals to initial
number of coins minus $coinsToIssue$.
This prevents the miner to take more coins, that is defined by emission rules.
Second, script checks that register $R3$ of $out$ contains current height and this height is greater, then height
kept in $R3$ register of spending input.
This prevents the miner to take use this output more then once per block.
Finally, it checks that $out$ have the same script, preventing miners to more coins then expected in the future.
Special case is required to stop emission - when this output contains less coins, than $oneEpochReduction$,
creation of a new output is not required.
