\section{Peer management protocol}\label{sec:peer-management-protocol}

\newcommand{\peers}{\mathcal{P}}

A \emph{peer} is a pair $(\term{addr}, \term{port})$,
where $\term{addr}$ is it IPv4/6 address and $\term{port}$ is its port.

A \emph{peer management structure} is a tuple $(G, B, C)$,
where $G$ is the set of \emph{good peers}, $B$ is the set of \emph{banned peers}, and
$C$ is the set of \emph{connected peers}, satisfying the following conditions:
$G \cap B = \emptyset$,
$C \subseteq G$,
$G \subseteq \peers$,
$B \subseteq \peers$.

\subsection{Peers penalization and blacklisting}\label{subsec:peers-penalization-and-blacklisting}

A \emph{penalty} is a tuple $(\term{descr}, \term{score})$, where $\term{descr}$ is a misbehavior
description and $\term{score}$ is a penalty score.
A \emph{penalty score} is a number defining how bad concrete kind of misbehavior is.

Penalties are divided into 4 categories:

\begin{itemize}
    \item{\em NonDeliveryPenalty} - applied when a peer did not deliver requested modifier in time
    \item{\em MisbehaviorPenalty} - applied when some modifier delivered by peer appeared to be invalid
    \item{\em SpamPenalty} - applied when a peer delivered non-requested modifier
    \item{\em PermanentPenalty} - applied to peers deviating from an actual network protocol
\end{itemize}

Once some penalty is applied a penalized peer is added to the penalty book.
A \emph{penalty book} is a mapping $\term{ip} \rightarrow (\term{score}, \term{ts})$, where $\term{ip}$
is a peer IP address, $\term{score}$ is an accumulated penalty score and $\term{ts}$ is a timestamp when a corresponding
peer was penalized last time.

Penalties of type $\term{NonDeliveryPenalty}$, $\term{MisbehaviorPenalty}$, $\term{SpamPenalty}$ are not applied
to the same peer repeatedly within a safe interval.

A \emph{safe interval} is a delay between penalties application.

Once some peer accumulates a critical penalty score it is added to the blacklist.
A \emph{blacklist} is a mapping $\term{ip} \rightarrow \term{ts}$, where $\term{ip}$ is a peer IP address
and $\term{ts}$ is a timestamp a peer is banned till.

The $\term{PermanentPenalty}$ is applied immediately and leads to a permanent ban of a peer

\subsection{Peer Discovery}\label{subsec:peer-discovery}

A peer discovery protocol requests new peers from a source and inserts them into
the set of good peers $G$.
Generally, a source may be another peer, a trusted central server or an untrusted communication
channel (e.g. IRC, Twitter, \ldots).
