\section{Consensus}

\dnote{describe, why did we chosen Proof-of-Work rather than PoS/PoXXX}

Ergo PoW algorithm was designed with 2 goals in mind:

\begin{itemize}
    \item{\em ASIC resistance } - the concentration of mining power to ASIC-equipped miners
    is a big security issue.
    ASIC-resistant PoW algorithm should allow miner to generate new blocks with non-negligible
    probability on commodity hardware.
    Equihash algorithm was chosen as a promising ASIC-resistant PoW algorithm.
    \item{\em pools resistance } - even if mining hardware is distributed between multiply parties,
    their union into mining pools leads to centralization of the network control in hands of the mining pool operators.
    Ergo PoW algorithm should disincentivize large mining pools, ensuring that mining pools are small (if possible).
\end{itemize}

\subsection{Equihash}

In Equihash a miner should find a solution of the generalized birthday problem: it should find
given list $L$ of $n$-bit words ${X_i}$, find $2^k$ distinct ${X_{i_j}}$ such that
XOR for all this words is 0. It is also required that this search was done via
Wagner's algorithm --- a PoW solution is considered valid only if it carries the footprint
of the iterative partial collisions, i.e, at step $r$, the first $jr/k+1$ bits should XOR to 0.
Difficulty control is implemented similar to regular PoW blockchains --- the hash of the block header
(including solutions) should be less than some predefined target $T$.

Mining process for Equihash PoW blockchain is defined in Alg. \ref{alg:eq:mining} and validation
process is defined in Alg. \ref{alg:eq:valudation}

\begin{algorithm}[H]
    \caption{Equihash mining}
    \label{alg:eq:mining}
    \begin{algorithmic}[1]
        \Function{solveEquihash}{$header$, $target$}
            \Let{$solutions$}{$findSolutions(header)$}
            \Let{$correctHeaders$}{$solutions.filter(s => hash(header.copy(solution = s)) < target)$}
            \If{$correctHeaders.nonEmpty$}

                \Return $correctHeaders$
            \Else
                \State Modify header by updating timestamp, transactions or other fields

                \Return $solveEquihash(modifiedHeader, target)$
            \EndIf
        \EndFunction

        \Function{findSolutions}{$header$}
            \Let{$seed$}{$hash(header.bytesWithoutPoW)$}
            \Let{$listSize$}{$2*2^{n / (k + 1)}$}
            \Let{$X$}{(0 to listSize).map(j => (hash(seed + j), j))}
            \For{r: 1 until k}
              \Let{$X$}(round(X, r))
            \EndFor
            \State find all possible collisions on the last $2n/k+1$ bits.

            \Return Sequence of solutions, where every solution is a sequence of indexes of words from X.
        \EndFunction

        \Function{round}{$X$, $r$}
        \State Sort the $X$ by values $X_j$ .
        \State Find all unordered pairs $(i, j)$ such that $X_i$ collides with $X_j$ on the first $r * n/(k+1)$ bits.

        \Return $(X_{i,j} = X_i$ xor $X_j, (i , j))$
        \EndFunction

    \end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
    \caption{Equihash validation}
    \label{alg:eq:valudation}
    \begin{algorithmic}[1]
        \Function{validateEquihash}{$header$, $solution$}
        \State check, that there is no duplicate indexes in solutions
        \Let{$X$}{solution.map(j => (hash(seed + j), j))}
        \State check algorithm binding - at step $r$, the first $rn/k+1$ bits should XOR to 0.
        \State check, that XOR for all X consists of 0 bits only

        \Return hash(header) < T
        \EndFunction
    \end{algorithmic}
\end{algorithm}

\subsection{Pool resistance}

This section contains several ideas how to prevent mining outsourcing:

\begin{itemize}
    \item{\em use private key } - ensure that private key was involved in mining process.
    Miner should include his public key and signature $Sig$ of all block fields to block header
    (or other parts of the block, like extension or block transactions)
    and all mining rewards goes to this public key.
    Equihash should use this signature as a $seed$ and also verifier should check, that indexes of solutions do
    not exceed $listSize$\footnote{This check is present in original Equihash algorithm in serialization process
    and is described in a paper in ``algorithm binding'' section, but our
current implementation lacks this check}.
    To ensure, that mining reward goes to public key used in block signing, all anyone-can-spend outputs should
    be collected to that public key (or may be it's better to use special `miner-can-spend` proposition
    that ensures that this box can only be spent in the last transaction of a block).
    Thus, for every search of Equihash solutions miner should sign a block.
    Pools might still be possible, but they should send a new signature for every Equihash operation that might
    be impossible for large pools. In assumption of $10^9$ Sol/s hashrate (that corresponds to current ZCash
    hashrate) large enough mining pool should should calculate $10^9$ signatures and send 64 Gb of data per second.

    \item{\em change search list requirements} - current Equihash implementation assumes that everyone can efficiently
    reconstruct the whole list miner used to find solutions. Changing this requirement might help in pool-protection.
    For example, if we will require that every search element should be a correct signature of a current block
    (instead of just numerical index), data transfer between pool and miner will be $2*2^{n / (k + 1)}~2^21$ times
    bigger than in the previous proposal.
    However, this naive change will significantly change PoW algorithm as far as the main work will be
    on signature calculation, rather than collision search.
    ASIC-resistance of this new protocol should be investigated.

    \item{\em search list as a secret} - when search list is not deterministic,
    pool-protection algorithm may be built on
    an idea, that miner is the only person who new the whole search list.
    One possible solution is to to include the root hash
    of a hash tree into block and change reward-taking condition for a miner, that he should provide a path in
    a hash tree to any leaf and use this leaf as a public key to take block reward.
    In such a case pool should enforce the whole search list by defining root hash otherwise miner will be able to
    steal a reward by providing a path to his own public key in the tree.
    
\item{\em inefficiency of the masked computations} --- one can also use the
    homomophity of elliptic curve multiplication to provide the asymmetry
    between puzzle solution and validation. In fact solving Generalized Birthday
    Problem is choosing $2^k$ linearly dependent $n$-dimensional vectors over
    $\mathbb{Z}/2\mathbb{Z}$ out of pseudorandom set. One can instead consider
    vectors with the coordinates in the elliptic curve group. Say, in 1D search for
    collisions for the words $x_i = sk_i - H(V||PK_i)$ with $PK_i=sk_iG$, and $G$
    being the group generator. The puzzle is to find such subset $J$ of indeces
    that $\sum_{j\in J} x_j = 0$. The solution is the list of corresponding
    values $PK_j$. Validator can ensure that $\sum_j PK_j =
    \sum_jH(V||PK_j)G$, and $sk_j$ may be used as secret keys for the
    spending transaction. Of course, a pool could provide the list of allowed $PK_i$,
    but given that point addition is much slower than number addition, it can
    result in search inefficiency. The hash size must be adjusted to match the
    group size. Another issue is potentially low length of $sk_i$. It
    may be possible to adjust it choosing the appropriate values of $n$ and
    $k$. In order to reduce number of pre-generated keys, one can allow nonce
    usage under the hash function. However, controlling the algorithm flow in this
    case is much harder (if possible).

\end{itemize}
